A molecular taxonomy of tumors independent of tissue-of-origin

### 2021-07-02 text/manuscript.Rmd
add some stuff about comparisons between models

The outcome of our model comparison with other published classification models 
in predicting tdeath showed kNN performing slightly better. However, for the 
purpose of predicting lifetime, all models are practically equivalent. One 
explanation for this is the cluster identity does not provide much new information 
from tissue-of-origin. Most of the cluster-specific rate ($A_{cl}$) peaked around 1 for 
all models – leaving the remaining variables ($A_{0}$, $A_{r}$, and $k_{tis}$), which are 
tissue-specific, to compute tdeath. While our study focused on somatic mutations, 
the incorporation of other types of omics data may help differentiate the classes 
within cancer type. Additionally, more work in solidifying the pathway model into 
cancer hallmarks could provide biologically meaningful distinction of the clusters.

>>>>

The outcome of our model comparison with other published classification models
in predicting tdeath showed kNN performing slightly better. However, for the
purpose of predicting lifetime within this dataset, all models are practically
equivalent. One possible explanation for this is the cluster identity does not
provide much new information from tissue-of-origin. However another possibility
is that because treatment is not specialized to cluster, the treatments are not
taking advantage of potential differences between clusters which might
dramatically change survival. Most of the cluster-specific rate ($A_{cl}$)
peaked around 1 for all models – leaving the remaining variables ($A_{0}$,
$A_{r}$, and $k_{tis}$), which are tissue-specific, to compute tdeath. While our
study focused on somatic mutations, the incorporation of other types of omics
data may help differentiate the classes within cancer type. Additionally, more
work in solidifying the pathway model into cancer hallmarks could provide
biologically meaningful distinction of the clusters. Finally, if treatments can
be specialized to biological information encoded in cluster, perhaps this could
drive dramatic improvements in survival among some clusters in the future.
